\section*{van Emde Boas Trees}
The van Emde Boas Tree data structure is recursive, this means we have to decide when to end the recursion. A natural starting point is to let the recursion end with leafs consisting of the 2 elements, $min$ and $max$, but since a tree with 3 elements will have a $TOP$ and $BOTTOM$ with a single element, that must also be supported. However, as stated in the note from G. Frandsen, and at the lectures, there is a point where you will gain better performance by reverting to an array and a liniar scan. Our implementation allows for this $threshold$ to be set upon creation of the tree. Quick testing showed that a threshold between 32-256 gave roughly the same performance. Higher or lower affected the query-time negatively.

\subsection*{Supported operations}
Our implementation support the following queries on a vEB tree:

\begin{itemize}
\item $uint32\_t \textbf{ veb\_insert}(uint32\_t index, void * data, vebtree * tree)$
\item $void \textbf{ veb\_delete}(uint32\_t index, vebtree * tree)$
\item $int32\_t \textbf{ veb\_findsucc}(uint32\_t index, void * data, vebtree *tree)$
\item $int32\_t \textbf{ veb\_findpred}(uint32\_t index, void * data, vebtree *tree)$
\end{itemize}

\textbf{delete\_min} and \textbf{find\_min} can both be implementeted with the above operations, by first calling \textbf{veb\_findsucc} on $0$, and if you want to delete it, call \textbf{veb\_delete} on the returned index.


\subsection*{Handling the leafs}
Our leafs are a simple array of elements and as such will not be explained in more detail than this part. The operations to \textbf{insert} and \textbf{delete} are a matter of inserting and deleting in the correct place in the array, this is done in constant time. The operations \textbf{find\_pred} and \textbf{find\_succ} are a matter of scanning the array from a certain posistion to find the first, if any, element that is before or after. The $min$ and $max$ is kept in a seperat pointer, so finding and accessing them is constant time. Since the arrays have a fixed length, independent from the size of the universe, \textbf{find\_pred}, \textbf{find\_succ} are also constant time.

\subsection*{Handling the recursive nodes}
The trees are build as described on the slides from the lectures - and \textbf{insert}, \textbf{delete} and \textbf{find\_succ} are all implemented as described on the slides as well. The operation \textbf{find\_pred}, is mostly identical to \textbf{find\_succ}, but obviously look for the first element preceeding the index. It's basicly a mirror of \textbf{find\_succ}.

\subsection*{Futher improvements}
Out leafs are an ordinary ``nodes'' with an array instead of continuing the search. One possibility could be to use a leaf size of 32 or 64, depending og the machine, and represent the elements as a bit array. Manipulating this will be extremly efficint, and then keep pointers to the actual data somewhere else.